---
title: "First look at Palmer Penguins"
editor_options: 
  chunk_output_type: console
---

# Introduction

How do bill sizes of penguins vary across species? And what happens if we don't take species into consideration?

## Packages

We will use the **tidyverse** packages for data wrangling and visualization and the **palmerpenguins** package for the data.

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(palmerpenguins)
```

## Data

The dataset we will visualize is called `penguins`. Let's `glimpse()` at it.

```{r}
#| label: glimpse
glimpse(penguins)
```

# Penguin bills

1.  Create a scatterplot of `bill_depth` vs. `bill_length`s of `penguin`s. Overlay a line of best fit. Describe the relationship between the two variables.

```{r}
#| label: bill-depth-width
ggplot(data = penguins,
       mapping = aes(x=bill_depth_mm, y=bill_length_mm)) +
  geom_point() + 
  geom_smooth(method="lm", se=FALSE)
```

Negative relationship between bill depth and length?

2.  Create a scatterplot of `bill_depth` vs. `bill_length`s of `penguin`s, colored by `species`. Overlay a line of best fit. Describe the relationship between the two variables for each of the species.

```{r}
#| label: bill-depth-width-species
ggplot(data = penguins,
       mapping = aes(x=bill_depth_mm,
                     y=bill_length_mm,
                     color = species)) +
  geom_point() + 
  geom_smooth(method="lm", se=FALSE)
```

Positive relationship between bill depth and length, within each of the species.

3.  Reflect on the seemingly contradictory findings from the two visualizations you've created. Which one do you believe more, and why? = OVB!
