---
title: "Student survey"
editor_options: 
  chunk_output_type: console
---

# Introduction

In this code along we'll work with a small but pretty "messy" survey data on favorite foods and some other information on school aged children.

## Packages

We will use the **tidyverse** for our analysis.

```{r}
#| message: false
library(tidyverse)
library(janitor)
```

## Data

The data are synthetic, so we ca make a few important points quickly.

# Analysis

-   Read the data in and inspect it.

```{r}
#| label: read-students-raw
students_raw <- read_csv("https://data-science-with-r.github.io/data/students-raw.csv")

students_raw
```

-   Fix the variable names.

```{r}
#| label: names
#| message: false

students_raw <- read_csv("https://data-science-with-r.github.io/data/students-raw.csv") |>
  janitor::clean_names()

students_raw
```

-   Handle NAs.

```{r}
#| label: nas
#| message: false

students_raw <- read_csv("https://data-science-with-r.github.io/data/students-raw.csv",
                         na = c("", "NA", "N/A")) |>
  janitor::clean_names()

students_raw
```

-   Inspect variable types and apply fixes where appropriate.

```{r}
#| label: types
students_raw <- read_csv("https://data-science-with-r.github.io/data/students-raw.csv",
                         na = c("", "NA", "N/A")) |>
  janitor::clean_names() |>
  mutate(age = if_else(age == 'five', "5", age),
         age = as.numeric(age))
students_raw
```

-   Inspect variable classes and apply fixes where appropriate. Save the resulting data frame as `students`.

```{r}
#| label: classes
students <- students_raw <- read_csv("https://data-science-with-r.github.io/data/students-raw.csv",
                         na = c("", "NA", "N/A")) |>
  janitor::clean_names() |>
  mutate(age = if_else(age == 'five', "5", age),
         age = as.numeric(age),
         meal_plan = as.factor(meal_plan))
```

-   Write out the `students` object to a CSV file in the data folder of your working directory.

```{r}
#| label: write-csv
# add code here
```

-   Read in the newly created `students.csv` and inspect the variable types and classes. Do you observe anything unexpected?

```{r}
#| label: read-csv
# add code here
```

-   Write out the `students` object to an RDS file in the data folder of your working directory.

```{r}
#| label: write-rds
# add code here
```

-   Read in the newly created `students.rds` and inspect the variable types and classes. How is this result different than the CSV file you read in?

```{r}
#| label: read-rds
# add code here
```
